---
output: github_document
---

# gglm: Grammar of Graphics for (Generalized) Linear Model Diagnostics

## Overview

`gglm` is a package that creates beautiful `ggplot2` diagonostic plots of generalized linear models that adhere to the Grammar of Graphics and are easy to use. 

## Installation 

```{r eval = FALSE}
# Currently, the best way to install is from GitHub.
devtools::install_github("graysonwhite/gglm")
```

## Examples

`gglm` has two main goals: (1) quickly create the four main diagnostics plots, similarly to when you call `plot()` on an `lm` or `glm` type object, and (2) produce diagnostic plots the align with the Grammar of Graphics by creating `ggplot2` layers that allow for easy plotting of particular model diagnostic plots. 

### Example 1: Quickly creating the four diagnostic plots

```{r}
library(gglm)
library(ggplot2)
data(mtcars) # Load example data
m1 <- lm(mpg ~ ., data = mtcars) # Create your model

gglm(m1)
```

### Example 2: Using the Grammar of Graphics

```{r}
library(gglm) 
library(broom) 
library(ggplot2)
data(mtcars) # Load example data
model <- lm(mpg ~ ., data = mtcars) # Create your model
model_tbl <- broom::augment(m1) # Turn model output into a tidy tibble

ggplot(data = model_tbl) +
  stat_fitted_resid()
```

Note that in this case, we need to `augment()` our model object into a tibble in order to supply it as the `data` argument in our `ggplot()` call. This is different from the `gglm()` function which takes in an object of type `lm` or `glm` in order to quickly show you your four main diagnostic plots.

## Function List

`gglm()` plots the four default diagnostic plots when supplied a glm. This function works similarly to `plot.lm()`, except that it displays the four diagnostic plots at once.

`stat_normal_qq()` produces a normal Q-Q plot. This function is very similar to `stat_qq()` from `ggplot2`. 

`stat_fitted_resid()` produces a fitted vs. residual plot. 

`stat_resid_hist()` produces a histogram of the distribution of the residuals. 

`stat_scale_location()`

`stat_cook()` vs. row labels and vs. leverage/(1-leverage). (Not yet built)

`stat_resid_leverage()` (Not yet built)
